SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations

### 2015-08-21 paper.tex

\begin{figure}[t!]
\centering
\includegraphics[width=12cm, height=6cm]{figures/teaser.eps}
\caption{ 
Conceptual illustration of robot states (projected onto the plane) with quantile levelset (shaded) for measuring the riskiness of
executing the current policy as distance from the levelset boundary.  In SHIF, supervisor demonstrations are only requested when risky states are encountered. 
}
\vspace*{-10pt}
\label{fig:dis_traveled}
\end{figure}

@@

\section{Problem Statement}
\subsection{Notation and Background}
{\color{blue} [-- TODO: SENSOR MODEL --]}
We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example of
high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or continuous in
nature\adnote{avoid filler words like in nature}. The environment is
modeled\adnote{avoid passive voice; sidd always asked me whenever i wrote that "X is done": "done by who? by jesus?"} to have dynamics that are stationary\adnote{why stationary? what does this mean?} and Markovian, such that the the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in \mathcal{U}$,
so that\adnote{this sentence already contained a so that; break long sentences} $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
When no confusion arises\adnote{what is confusion arising}, we denote the probability density over the initial state also by $p:\mathcal{X}\to
\mathbb{R}$. By a trajectory, we mean \adnote{new par, a trajectory is a finite ...}a finite series of pairs of $T$ states visited and corresponding
control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
At times we will also consider trajectories in state space only\adnote{this makes you seem floppy; do we need this? if so maybe denot by something else, like $\bar{tau}$ and call it a full trajectory vs a state trajectory}, in which case a trajectory corresponds
to a sequence of states $\tau = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.

@@

\caption{Data is sampled from a Gaussian Mixture Model and in Fig. \ref{fig:subfigure1}, the red points are those that the trained policy, $\pi_{theta}$ will mis-predict. In Fig. \ref{fig:subfigure2} the One Class SVM is fit to the data and tries to estimate the areas of low risk (the light green region), while it is able to estimates the area where the majority of the data lies it also encloses the points the trained policy is mis-predicting. In Fig. \ref{fig:subfigure3}, the Risk Sensitive One Class SVM is able to effectively remove the red points from the region of low risk.}
\label{fig:support_example}
\end{figure*}

>>>>

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/teaser.pdf}
\caption{ 
Illustrations of the different examples we evaluated our algorithm, SHIV, on. A) Driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track. B) Grasping in clutter experiment in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not moving the red square objects off the gray boundary representing a table. C) A experiment on the Da Vince Research Kit to learn a controller from a surgeon's demonstrations of correcting a needle before suturing in surgery. 
}
\vspace*{-10pt}
\label{fig:dis_traveled}
\end{figure}

@@

\caption{An illustrative example of different active learning techniques. The shaded and empty circles represent different labeled classes $0$ and $1$. The red empty circles represent label $1$, but are encountered on a different distribution then what was trained on. As illustrated, Confidence and Query by Committee methods measure states far away from the decision boundary of the estimator as low risk, however novelty detection methods measure the level of risk as how far a point is from the trained data. Our modified risk method attempts to measure risk both as a function of how far it is from data trained on and the decision boundary of the estimator. }
\label{fig:support_example}
\end{figure*}

\section{Problem Statement}
\subsection{Notation and Background}
We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example of
high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or continuous in
nature\adnote{avoid filler words like in nature}. The environment is
modeled\adnote{avoid passive voice; sidd always asked me whenever i wrote that "X is done": "done by who? by jesus?"} to have dynamics that are stationary\adnote{why stationary? what does this mean?} and Markovian, such that the the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in \mathcal{U}$,
so that\adnote{this sentence already contained a so that; break long sentences} $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
When no confusion arises\adnote{what is confusion arising}, we denote the probability density over the initial state also by $p:\mathcal{X}\to
\mathbb{R}$. By a trajectory, we mean \adnote{new par, a trajectory is a finite ...}a finite series of pairs of $T$ states visited and corresponding
control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
At times we will also consider trajectories in state space only\adnote{this makes you seem floppy; do we need this? if so maybe denot by something else, like $\bar{tau}$ and call it a full trajectory vs a state trajectory}, in which case a trajectory corresponds
to a sequence of states $\tau = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.

@@
